Best Practices for Multiple Alchemical Free Energy Calculations [Article v\versionnumber]

### 2025-06-06 paper/manuscript.tex
move iLLE subsubsection to main text

@@

\subsubsection{predicted iLLE plots}
Best-practices for reporting predicted affinities retrospectively have been outlined, however using free energy methods prospectively where possibly none, one or only a few experimental datapoints for the set have associated energies might be available can be more difficult if any supporting statistics will not be possible or meaningful for a small set. Lipohilic ligand effciency (LLE or LipE) plots are typically used in drug discovery for understanding the relationship between lipophilic-driven binding affinity for series of compounds. Predicted or measured LogD or LogP on the x-axis and measured potency on the y-axis, typically with diagonal y=x+C lines used to indicate where compounds are achieving better/worse binding due to specific or polar interactions. Using \textit{in silico} iLLE plots, with predicted affinities and predicted LogP or LogD can be helpful to visually present free energy results with limited experimental data.

>>>>

Best-practices for reporting predicted affinities retrospectively have been outlined, however using free energy methods prospectively where possibly none, one or only a few experimental datapoints for the set have associated energies might be available can be more difficult if any supporting statistics will not be possible or meaningful for a small set. Lipohilic ligand effciency (LLE or LipE) plots are typically used in drug discovery for understanding the relationship between lipophilic-driven binding affinity for series of compounds. Predicted or measured LogD or LogP on the x-axis and measured potency on the y-axis, typically with diagonal y=x+C lines used to indicate where compounds are achieving better/worse binding due to specific or polar interactions. Using \textit{in silico} iLLE plots, with predicted affinities and predicted LogP or LogD can be helpful to visually present free energy results with limited experimental data.

@@
